### 2022-07-07 chapters/benchmarking/draft.tex
fix : repeated paragarpahs

Furthermore, between the exploratory experiment and the published results, there may have been the appearance of new candidates as well as the evolution of others.
As a result, it is not only necessary to assure the "reproducibility" of the results, but it is also essential to provide room for new candidates.
As a result, we'd like to present "Extension," a new approach for leveraging experimentation.
The ability to give not only the tools needed to replicate the tests but also to integrate more candidates, workloads, or important key performance indicators.

This chapter covers ways to overcome empirical analysis challenges in energy consumption studies. First, we'll go through the three components of a successful benchmark within the energy consumption experiment. Section 1 will therefore concentrate on the "reproducibility" issue and how to deliver reproducible experiments without interfering with the energy measurement. Section 2 will discuss accuracy in software energy consumption. Finally, Section 3 will discuss tools for introducing new candidates, workloads, or other key performance indicators.

Regarding the "representativeness" of the benchmarks, we will elaborate in the section entitled Perspectives.

@@

\paragraph{Virtual Machines}
FThe very first choice should be to use \emph{Virtual Machines} (VM), which allow researchers to select the most appropriate tools, software, and operating system that they are most comfortable with without incurring the cost of changing the actual working environment, giving them more control over dependencies and the execution environment.
Furthermore, adopting a VM addresses the \emph{replication crisis} since virtual images allow even the most sophisticated architecture to be simply replicated by instantiating a copy of the image.

@@

Yet, as seen in Figure 3.3, Docker increased the execution duration of the benchmark by 50 seconds, increasing energy usage.
According to the authors, this overhead is primarily caused by the Docker deamon and not by the fact that the

>>>>

Furthermore, between the exploratory experiment and the published results, there may have been the appearance of new candidates as well as the evolution of others.
As a result, it is not only necessary to assure the "reproducibility" of the results, but it is also essential to provide room for new candidates.
As a result, we'd like to present "Extension," a new approach for leveraging experimentation.
The ability to give not only the tools needed to replicate the tests but also to integrate more candidates, workloads, or important key performance indicators

@@

\paragraph{Virtual Machines}
The very first choice should be to use \emph{Virtual Machines} (VM), which allow researchers to select the most appropriate tools, software, and operating system that they are most comfortable with without incurring the cost of changing the actual working environment, giving them more control over dependencies and the execution environment.
Furthermore, adopting a VM addresses the \emph{replication crisis} since virtual images allow even the most sophisticated architecture to be simply replicated by instantiating a copy of the image.

@@

### 2022-07-07 chapters/benchmarking/experiment.tex
fix : repeated paragarpahs

\subsubsection{Workload}
Our choice for the benchmarks was based on two criterions.

First, \textbf{scalability} : We wanted to gather the highest possible amount insights (regarding time spent for the experiment, therefore we wanted some benchmarks who can scale according to the number of PUs and can fulfill different scenarios.
Second criterion is \textbf{representativeness} : as mentioned in the challenges, a workload has to be representative otherwise the experiment would be inconsistent \cite{stephen_evaluate_2012}.
To satisfy those criterions we went through state of the art and looked for the most used benchmarks for testing the performance of the hardware, and then we selected the scalable ones.
%%%%%% 
We picked the benchmarks based on two criteria.

First, \textbf{scalability}: We wanted to learn as much as possible about the experiment in the time we had, so we needed some benchmarks that could grow or shrink with the number of PUs and work in different situations.

The second criterion is whether or not the workload is \textbf{representative}. As stated in the challenges, a workload must be representative or the experiment would be inconsistent~\cite{stephen_evaluate_2012}.

>>>>

\subsubsection{Workload}

We picked the benchmarks based on two criteria.

First, \textbf{scalability}: We wanted to learn as much as possible about the experiment in the time we had, so we needed some benchmarks that could grow or shrink with the number of PUs and work in different situations.
The second criterion is whether or not the workload is \textbf{representative}. As stated in the challenges, a workload must represent the production enviromenet or the experiment would be inconsistent~\cite{stephen_evaluate_2012}.

### 2022-07-07 chapters/programming_languages/programming_languages.tex
fix : repeated paragarpahs

\chapter{Energy footprint of programming languages}
\label{chapter:porgramming_langauges}
In this chapter, we discuss the impact of the choice of the programming language on the energy consumption of the resulting software.
To do so, we suggest to start with the general micro benchmarking and see how each programming languages interact with the CPU/Memory.

The ultimate goal of this chapter is to provide a guideline on which programming language the developers should chose based on the charecteristics of the project in order to minimize the energy foot print of their product.
No answer is evidedent for a such question. However, we can extract some feartures of each programming langues such as
\begin{itemize}
    \item performance
    \item community support
    \item scalability
    \item energy consumptiom
    \item memory usage
    \item etc
\end{itemize}

first we will start but analysing the behaviour of the general purpose programming langauges with some micro benchkaks, principally for the CLBG game and others from rosetta code base

As we have seen in the previous chapter, one of the most important feature of a test is to be \textbf{representative}.
Therefore, we extend this study to some real-life use case, and the following sections below provide two case studies.
\section{Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}
\section{web Frameworks}
\import{\currfiledir/web_frameworks}{web_frameworks}

>>>>

\chapter{Energy footprint of programming languages}
\label{chapter:porgramming_langauges}
In this chapter, we talk about how the programming language affects how much energy the software consumes.We suggest starting with general microbenchmarking and watching how each programming language performs with the CPU and memory.The main goal of this chapter is to advise developers on how to choose a programming language based on their project's needs in order to make their product use the least amount of energy possible. For such a question, no answer is evidedent.But there are some features we can take from each programming language, such as: 
\begin{itemize}
    \item performance
    \item community support
    \item scalability
    \item energy consumptiom
    \item memory usage
\end{itemize}

As we saw in the last chapter, one of the most important things about a test is how well it \textsc{represents} the production environment. Therefore, we extend this study to include real-world use cases, with two case studies provided in the parts that follow. 
\section{Remote Procedure Call Frameworks}
\import{\currfiledir/rpc}{rpc}
\section{web Frameworks}
\import{\currfiledir/web_frameworks}{web_frameworks}
